USAMS Hybrid Source Summary

### 2021-01-24 hgis_summary.Rmd
Fix typos.

2020-12-11 - Open split flow reduction. Test flow controller for helium, adjust
needle valves to allow lower CO2 flows. Measure blanks of target, helium, CO2
and dilluted CO2.

2020-12-04 - Measure blank contributions of target/source, helium, CO2, and
dilluted CO2. Install flow controller for helium.

@@

2020-11-03 - Troubleshoot low currents, measure dilluted and pure live and dead
gas.

@@

2020-10-06 - Dillution tests of live and dead gas. Test stability of currents
over time.

>>>>

2020-12-11 - Open split flow reduction. Test flow controller for helium, adjust
needle valves to allow lower CO2 flows. Measure blanks of target, helium, CO2
and diluted CO2.

2020-12-04 - Measure blank contributions of target/source, helium, CO2, and
diluted CO2. Install flow controller for helium.

@@

2020-11-03 - Troubleshoot low currents, measure diluted and pure live and dead
gas.

@@

2020-10-06 - Dilution tests of live and dead gas. Test stability of currents
over time.
